\huge A Usability Evaluation of Tor Launcher

### 2017-03-16 pets2017-paper/pets2017-paper.tex
More on clark2007usability.

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
There are some earlier usability studies that focused on installation and use,
but not on setting up Tor Browser.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately}, in 2010,
estimated how much Tor's added latency harms usability.
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancelation rate,''
the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
% \cite{dingledine2009performance}
Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.

>>>>

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
There are some studies that evaluated earlier forms of the browser,
without a particular focus on configuration.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately}, in 2010,
estimated how much Tor's added latency harms usability
(considered separately from user interface concerns).
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancelation rate,''
the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
% \cite{dingledine2009performance}
In 2007, Clark et~al.~\cite{clark2007usability}
used cognitive walkthroughs to evaluate four
methods of web browsing over Tor
(all of which have since been superseded by Tor Browser and Tor Launcher).
Evaluating each method against a set of guidelines,
they found that none were fully satisfactory,
though the ones that used automatic configuration did better.
Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.
